Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
revised CEGIS 2nd approach

We investigate two different approaches of integrating solution generalisation 
into CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which 
enables abstraction refinement inside the CEGIS loop. 
\item[2.] The second approach relies on computing a completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the generalisation step is given as an incremental
increase of precision and sampling rate.
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. Note that, 
as mentioned at the beginning of the section, 
we consider the reference signal to be 0.
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$.

We compute the coefficients for $K$ 
in the domain $\mathbb{R}<I,F>$.

@@

\subsubsection{Computing the reachable states}

In order to compute the set of reachable states we find 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
The closed-loop state-space system has to be unwound up to a given 
depth $\overline{k}$ to ensure that $\phi_{safety}$ holds.

\todo{discuss the completeness threshold computation}

\subsubsection{Controller synthesis}

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}
and consists of five stages, as described below:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$.

@@

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not be violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$.

>>>>

We investigate two different approaches of integrating solution generalisation 
with CEGIS:
\begin{itemize}
\item[1.] The first approach uses abstract acceleration to compute the set of reachable states, which enables it to perform abstraction refinement inside the CEGIS loop (see Sec~\ref{sec:CEGIS-abstraction-refinement}). 
\item[2.] The second approach relies on computing a 
completeness threshold $k$ for each loop such that it is sufficient to 
unroll the corresponding loop $k$ times. For this approach the 
generalisation step is given as an incremental
increase of precision and sampling rate (see Sec.~\ref{sec:CEGIS-precision-incrementation}).
\end{itemize}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. Note that, 
as mentioned at the beginning of the section, 
we consider the reference signal to be 0.
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.

@@

%\subsubsection{Controller synthesis}

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not be violated for any $k>\overline{k}$. 
Then, it is sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.

Next, we describe the five stages from Fig.~\ref{fig:CEGIS-precision-increment}:

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a $k$ and a sampling rate. The check that this assumptions were sound 
will be performed later by the {\sc complete} and {\sc sampling} 
validation stages.

@@

4. This stage checks that the current  $k$ 
is large enough to ensure that the boundaries are not be violated for any $k'>k$.
In order to verify this, we compute the 
completeness threshold $\overline{k}$ for the current candidate $K$ 
and check that $k{\leq}\overline{k}$. 
\todo{discuss the computation of the completeness threshold}
